The Stakes of Scrying: \texttt{\string.\string^} dotket and the Seer Proposal

### 2024-01-11 mss.tex
Move footnote to main body.

The concerns with \dotket~go deeper than memoization however, despite that being the only known major concrete issue.\footnote{There is also some complexity in the runtime when jetting the metacircular interpreter.}  Conceptually, the fact that a Mock computation has implicit external dependencies makes the pure-functional nature of the system more fragile—the memoization issue is downstream of this fragility.

Morally and aesthetically, the fact that Nock makes no assumptions about any of its contents is part of the magic of Urbit.  Nock is a true functional programming language with no implicit external dependencies at all, and no constraints on the nouns it operates on.  Anything that pollutes this vision is potentially harmful to the environment Urbit creates for programs and their authors.  Mock's implicit dependency on the namespace makes Nock context-dependent instead of context-independent, as it should be.\footnote{There's also an issue that userspace code does not have access to raw Nock, only Mock.  The Hoon compiler willingly outputs Nock 12 instructions when handed a \dotket~rune, and there is no means for userspace code to signal that it will refrain from using Nock 12.}

>>>>

The concerns with \dotket~go deeper than memoization however, despite that being the only known major concrete issue.\footnote{Some complexity is introduced in the runtime when jetting the metacircular interpreter.}  Conceptually, the fact that a Mock computation has implicit external dependencies makes the pure-functional nature of the system more fragile—the memoization issue is downstream of this fragility.

Morally and aesthetically, the fact that Nock makes no assumptions about any of its contents is part of the magic of Urbit.  Nock is a true functional programming language with no implicit external dependencies at all, and no constraints on the nouns it operates on.  Anything that pollutes this vision is potentially harmful to the environment Urbit creates for programs and their authors.  Mock's implicit dependency on the namespace makes Nock context-dependent instead of context-independent, as it should be.  A related issue is that userspace code does not have access to raw Nock, only Mock.  The Hoon compiler willingly outputs Nock 12 instructions when handed a \dotket~rune, and there is no means for userspace code to signal that it will refrain from using Nock 12.
